---
title: "Playing with Trees"
output: html_notebook
---
```{r, setup, include=FALSE}
library(tidytree)
library(treeio)
library(ggtree)
knitr::opts_knit$set(root.dir="D:/Data/200502_ncov")

```


Ok - it looks like there are a couple packages in R specifically for generating and playing with trees

tidytree, ggtree look specifically good (because tidyverse)

First - I'll grab newick and tsv from JHU nextstrain version

```{r}
#dir()
fulltree=as_tibble(read.newick("nextstrain_ncov_global_tree.nwk"))
```
Ok - tree loaded, now lets find the hopkins ones
```{r}

hoptree=fulltree %>%
  filter(grepl("MD-HP", label))

hopparents=fulltree %>%
  filter(parent %in% hoptree$parent) %>%
  filter(!grepl("NODE", label))

#ggtree(as.treedata(hopparents))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
